### 2017-06-10 paper.tex
updates the rule order

The converse of this rule is to license your own lessons in a similar open manner,
and to make them discoverable.
For example,
when lessons are published (Rule~7),
make sure that have the usual keywords in their bibliographic entries
and HTML page headers.

@@

Doing this shifts the instructor's burden from writing to finding and synthesizing,
both of which are easier if lessons have been designed by people with a shared world-view (Rule~6),
and if lessons clearly signal what they cover (Rule~1).
In particular,
if lessons reference specific points in the model curriculum guidelines promulgated by many professional societies,
it can be much easier for people to find them and integrate them.

@@

>>>>

@@

Doing this shifts the instructor's burden from writing to finding and synthesizing,
both of which are easier if lessons have been designed by people with a shared world-view (Rule~4),
and if lessons clearly signal what they cover (Rule~1).
In particular,
if lessons reference specific points in the model curriculum guidelines promulgated by many professional societies,
it can be much easier for people to find them and integrate them.

@@

The converse of this rule is to license your own lessons in a similar open manner,
and to make them discoverable.
For example,
when lessons are published (Rule~6),
make sure that have the usual keywords in their bibliographic entries
and HTML page headers.
